---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# dod

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/dod)](https://CRAN.R-project.org/package=dod)
[![R-CMD-check](https://github.com/dankelley/dod/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/dankelley/dod/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of dod is to make it easier to download various types of oceanographic
data from common sources such as BATS, NOAA, MEDS, BBMP. Some similar functions
exist in the oce package, but the intention is to retire them as dod matures,
because building oce is difficult for some users, and CRAN policies dictate
against frequent updates.

## Installation

You can install the development version of dod from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dankelley/dod")
```

## Example

The following example shows how to (1) download an index of CTD data files
resulting from observations made as part of the BBMP program in the present
year and then (2) use functions in the oce package to read and plot the 
first CTD profile of year 2024.

```{r example}
library(dod)
library(oce)
# Note: cannot specify year=2025 because the URL is differently constructed
index <- dod.ctd.bbmp.index(year = "2024")
ctdFile <- dod.ctd.bbmp(year = index$year[1], ID = index$id[1], direction = "DN")
# Use oce to read, summarize and plot the data.
ctd <- read.netcdf(ctdFile) |>
    rename() |>
    as.ctd()
# Plot some biochemistry variables
par(mfrow = c(2, 2))
plotProfile(ctd, "SA")
plotProfile(ctd, "CT")
plotProfile(ctd, "oxygen")
plotProfile(ctd, "chlorophyllA")
```

PS. This `README.md` file was created on `r Sys.Date()` by rendering the
`README.Rmd` file with `devtools::build_readme()`.
